Critical Temperature of Superconductors YBCO and BSCCO

### 2014-11-21 Draft.tex
intro

%certain types of metals at temperatures around 10 K were found to exhibit superconductivity, that is, their electrical resistance became zero. 
%The temperature at which this loss of resistance occurs is called the critical temperature.

\section{Ordinary text and paragraphs}

To typeset a paragraph of ordinary text, just type the text in your source
file like this. Put line breaks
wherever
you
want, and don't      worry      about      extra      spaces      between      words, which \LaTeX\ will ignore.  You can almost always trust \LaTeX\ to make your paragraphs look good, with neatly justified margins.  % Long lines of text are fine, since most editing programs will wrap them automatically.

@@

\section{Math symbols}

>>>>

\section{Aims}
\begin{enumerate}
\item To determine the critical temperature of YBCO and BSCCO.
\end{enumerate}

\section{Procedure}
The YBCO and BSCCO superconductors were obtained from Colorado Superconductor Inc. Each superconductor  is contained in a brass casing with two pairs of leads. One pair is attached to the current source and the other pair was used to measure voltage across the superconductor. The casing also contains a thermocouple, which has a resistance that varies with temperature. We measure the voltage across the thermocouple to find the temperature of superconductor. We used different methods to measure the critical temperature of the two superconductors.

For the YBCO, we connected to an alternating current source of 1 mA. 
\section{Results and Analysis}

\section{Discussion}

\section{Conclusion}
To typeset a paragraph of ordinary text, just type the text in your source
file like this. Put line breaks
wherever
you
want, and don't      worry      about      extra      spaces      between      words, which \LaTeX\ will ignore.  You can almost always trust \LaTeX\ to make your paragraphs look good, with neatly justified margins.  % Long lines of text are fine, since most editing programs will wrap them automatically.

@@
